### Q0: Sampling and Distribution

You are studying the population of a specific type of marine algae in different locations. Assume the algal density is normally distributed. You take samples from two locations (Location A and Location B) to compare the algae populations. Generate synthetic data to represent the algal density (individuals per square meter) at these two locations. Assume a mean density of 200 and 220 individuals/m^2 with a common standard deviation of 20 individuals/m^2 for both locations, with 50 samples from each location.


```{r}

locA_meandens <- 200
locB_meandens <- 220
st_dev <- 20
sample_size <- 50

locA_synthdata <- round(rnorm(n = sample_size, mean = locA_meandens, sd = st_dev))
locB_synthdata <- round(rnorm(n = sample_size, mean = locB_meandens, sd = st_dev))

all_data <- data.frame(
  Location = rep(c("A", "B"), each = sample_size),
  Algal_Density = c(locA_synthdata, locB_synthdata))

LocationA <- rnorm(50, mean = 200, sd = 20)
LocationB <- rnorm(50, mean = 220, sd = 20)

library(ggplot2)
ggplot() +
geom_histogram(aes(x = LocationA, y = after_stat(count / sum(count))), bins = 10, alpha = 0.4,fill = "blue", color = "black") +
  geom_vline(xintercept = locA_meandens, color = "green", linetype = "dashed", size = 1) +
  geom_vline(xintercept = locA_meandens - st_dev, color = "yellow", linetype = "dashed", size = 1) +
  geom_vline(xintercept = locA_meandens + st_dev, color = "yellow", linetype = "dashed", size = 1) +
  geom_vline(xintercept = locA_meandens - st_dev*2, color = "red", linetype = "dashed", size = 1) +
  geom_vline(xintercept = locA_meandens + st_dev*2, color = "red", linetype = "dashed", size = 1) +
  labs(title = "Histogram of Gaussian Samples",
       x = "Location A",
       y = "Individuals / m^2") +
  theme_minimal()
               
ggplot() +
geom_histogram(aes(x = LocationB, y = after_stat(count / sum(count))), bins = 10, alpha = 0.4,fill = "blue", color = "black") +
  geom_vline(xintercept = locB_meandens, color = "green", linetype = "dashed", size = 1) +
  geom_vline(xintercept = locB_meandens - st_dev, color = "yellow", linetype = "dashed", size = 1) +
  geom_vline(xintercept = locB_meandens + st_dev, color = "yellow", linetype = "dashed", size = 1) +
  geom_vline(xintercept = locB_meandens - st_dev*2, color = "red", linetype = "dashed", size = 1) +
  geom_vline(xintercept = locB_meandens + st_dev*2, color = "red", linetype = "dashed", size = 1) +
  labs(title = "Histogram of Gaussian Samples",
       x = "Location B",
       y = "Individuals / m^2") +
  theme_minimal()
```

### Q1: Data Cleaning

Check your dataset for any outliers. 

```{r}
### Write your code here

threshold <- 2  # Adjust as needed

# Identify outliers in Location A

outliers_A <- locA_synthdata[abs(locA_synthdata - locA_meandens) > threshold * st_dev]

# Identify outliers in Location B
outliers_B <- locB_synthdata[abs(locB_synthdata - locB_meandens) > threshold * st_dev]

print(outliers_A)
print(outliers_B)


  


```


### Q2: Visualization and Kernel Density Estimation (KDE)

Plot a Kernel Density Estimation (geom_density plot) to visualize the distribution of algal densities at both locations. 

```{r}
### Write your code here
ggplot(all_data, aes(x = Algal_Density, fill = Location)) +
  geom_density(alpha = 0.5) +
  labs(title = "Kernel Density Estimation of Algal Densities",
       x = "Algal Density (individuals/m^2)",
       y = "Density") +
  theme_minimal()

```

### Q3: Binomial Distribution
Suppose in a new survey, at each location, you take 10 random samples and in each sample, you identify whether a particular species of marine algae is present or not. Assume the probability of finding this species in a sample is 0.7 at Location A and 0.5 at Location B.

Simulate this scenario using a binomial distribution, and compare the probability of finding the species in at least 7 out of 10 samples at both locations.

```{r}
### Write your code here

probsA <- dbinom(7, size=10, prob=0.7)
probsB <- dbinom(7, size=10, prob=0.5)

print(probsA)
print(probsB)

#There is more than 2x the chance of finding the species in at least 7/10 samples at Location A than Location B.
```

### Q4: Poisson Distribution
Imagine a scenario where you are studying the occurrences of a particular rare marine event, such as the sighting of a rare marine species, over a set period at a specified location. Assume the average rate of occurrence is 3 per month.

Utilize a Poisson distribution to calculate the probability of observing exactly 5 occurrences in a month, and the probability of observing 3 or fewer occurrences in a month.

```{r}
### Write your code here
avg_ROO <- 3  # average rate of occurrence
k_5 <- 5     # number of occurrences for the first calculation

# Probability of observing exactly 5 occurrences
prob_5 <- dpois(k_5, avg_ROO)

# Probability of observing 3 or fewer occurrences
k_3_or_fewer <- 0:3  # values for k from 0 to 3
prob_3_or_fewer <- sum(dpois(k_3_or_fewer, avg_ROO))

# Print the results
cat("Probability of observing exactly 5 occurrences:", prob_5, "\n")
cat("Probability of observing 3 or fewer occurrences:", prob_3_or_fewer, "\n")

# there is a much higher likelihood of observing 3 or fewer occurrences (0.65) in a month than 5 occurrences (0.11).

```

### Q5: 
consider the following two lists. 

```{r}
list1 <- c(44.40, 47.70, 65.59, 50.71, 51.29, 67.15, 54.61, 37.35, 43.13, 45.54, 62.24, 53.60, 54.01, 51.11, 
           44.44, 67.87, 54.98, 30.33, 57.01, 45.27, 39.32, 47.82, 39.74, 42.71, 43.75, 33.13, 58.38, 51.53, 
           38.62, 62.54, 54.26, 47.05, 58.95, 58.78, 58.22, 56.89, 55.54, 49.38, 46.94, 46.20, 43.05, 47.92, 
           37.35, 71.69, 62.08, 38.77, 45.97, 45.33, 57.80, 49.17, 52.53, 49.71, 49.57, 63.69, 47.74, 65.16, 
           34.51, 55.85, 51.24, 52.16, 53.80, 44.98, 46.67, 39.81, 39.28, 53.04, 54.48, 50.53, 59.22, 70.50, 
           45.09, 26.91, 60.06, 42.91, 43.12, 60.26, 47.15, 37.79, 51.81, 48.61, 50.06, 53.85, 46.29, 56.44, 
           47.80, 53.32, 60.97, 54.35, 46.74, 61.49, 59.94, 55.48, 52.39, 43.72, 63.61, 44.00, 71.87, 65.33, 
           47.64, 39.74)

list2 <- c(44.34, 48.85, 41.30, 39.79, 30.73, 44.32, 33.23, 19.98, 39.30, 58.78, 36.37, 54.12, 20.73, 44.17, 
           52.79, 49.52, 46.59, 35.39, 32.25, 29.64, 46.76, 30.79, 37.64, 41.16, 72.66, 35.22, 48.53, 46.17, 
           30.57, 43.93, 66.67, 51.77, 45.62, 38.66, 14.20, 61.97, 23.09, 56.10, 73.64, 23.34, 55.53, 41.07, 
           21.42, 22.28, 20.98, 37.04, 23.07, 55.32, 76.50, 25.69, 56.82, 56.54, 49.98, 29.87, 43.21, 40.79, 
           53.44, 39.41, 59.65, 39.38, 60.79, 29.26, 26.10, 93.62, 38.75, 49.47, 54.55, 37.74, 52.75, 50.53, 
           41.77, 45.98, 44.49, 76.93, 33.88, 28.56, 45.57, 49.66, 51.55, 38.12, 29.05, 63.95, 39.76, 32.02, 
           41.46, 42.04, 61.65, 46.27, 56.31, 37.51, 48.22, 40.13, 46.42, 31.57, 25.34, 74.96, 54.01, 26.23, 
           35.83, 27.22)

```

These list were generated using the following code
```{r}
set.seed(123)  # Setting a seed for reproducibility
list1 <- round(rnorm(100, mean = 50, sd = 10), 2)  # Generating 100 values from a normal distribution
list2 <- round(rnorm(100, mean = 45, sd = 15), 2)  # Generating 100 values from another normal distribution
```

Compare the distributions of these two lists to determine if they originate from the same distribution or from different distributions.

1. Use geom_density to create a density plot for each list on the same graph. Use different colors to distinguish between the two lists:
```{r}
### Write your code here
mean(list1)
mean(list2)

df <- data.frame(value = c(list1, list2),
                 group = rep(c("List 1", "List 2"), each = 100))

# Create a density plot
ggplot(df, aes(x = value, fill = group)) +
  geom_density(alpha = 0.5) +
  labs(title = "Density Plot - Comparison of List 1 and List 2",
       x = "Values", y = "Density") +
  scale_fill_manual(values = c("List 1" = "blue", "List 2" = "red")) +
  theme_minimal()

```

Examine the plot you have generated. Do you think list1 and list2 come from the same distribution or different distributions? Why?
Write down your observations and reasoning.


* Write your answer below

No, I do not think these two lists come from the same distribution. The lists have different means and different distributions. 
